Are We Reusing Outdated and License-violating Code \newline from Stack Overflow?

### 2017-01-26 cloneoverflow-latex/cloneoverflow.tex
Added TXL problems
Update the clone stats of the 4 configurations.
Add "blocks" to NiCad settings.

\begin{table}
	\centering
	\caption{Configurations of Simian and NiCad}
	\label{t:param_tuning}
%	\resizebox{\columnwidth}{!}{%
	\small
	\begin{tabular}{l|p{5.5cm}}
		\hline 
		Tool & Parameters \\
		\hline
		$S_D$ &  threshold=6, ignoreStringCase, \newline ignoreCharacterCase, ignoreModifiers \\ 
		\hline
		$S_E$ & threshold=5, ignoreIdentifiers, \newline ignoreIdentifierCase, ignoreStrings, \newline ignoreCharacters, ignoreSubtypeNames, \newline balanceSquareBrackets  \\ 
		\hline 
		$N_D$ & MinLine=10, MaxLine=1000, UPI=0.30 \\
		\hline
		$N_E$ & MinLine=5, MaxLine=604, UPI=0.20, \newline blind renaming, literal abstraction \\ 
		\hline 
	\end{tabular} %
%}
\end{table}

@@

\begin{table}
	\centering
	\caption{Statistics of clones found between Stack Overflow and Qualitas projects using Simian (\textit{S}) and NiCad (\textit{N}) with default (\textit{D}) and EvaClone (\textit{E}) configurations}
	\label{tab:raw_stats}
	\small
	\resizebox{\columnwidth}{!}{%
		\begin{tabular}{l|r|r|r|r}
			\hline
			Stats & \multicolumn{1}{c|}{$S_D$} & \multicolumn{1}{c|}{$S_E$} & \multicolumn{1}{c|}{$N_D$} & \multicolumn{1}{c}{$N_E$} \\
			\hline
			Snippets & 1,086 & 1,530 & 1,240 & 12,886 \\
			Total C$_{\textrm{\textit{pairs}}}$ & 67,570 & 63,372,599 & 229,176 & 206,760,077 \\
			Avg.~C$_{\textrm{\textit{pairs}}}$ & 62 & 41,447 & 185 & 16,047 \\
			Avg.~C$_{\textrm{\textit{size}}}$ & 7.72 & 4.79 & 9.64 & 5.32 \\
			Avg.~C$_{\textrm{\textit{\%}}}$ & 29\% & 28\% & 25\% & 21\% \\
			\hline
		\end{tabular} %
	}
\end{table}

@@

Agreed clone pairs are clone pairs that pass Bellon's good- or ok-match criteria and selected for manual investigation. Similar to the original study, we select a threshold \textit{p} of 0.7 for both \textit{good} and \textit{ok} pairs \cite{Bellon2007}. %The number of projects processed by the clone detection tools are listed in \Cref{tab:projects_missing}. 
We encountered NiCad failures with a few Qualitas projects. 
%\FIXME{Reported the errors to NiCad creator. Cordy said it might be a long-path problem. Should we try fixing?}  
$N_D$ could not detect clones in Hibernate due to clustering errors. $N_E$ generated renaming errors for 5 projects including Vuze, Hibernate, Myfaces, Netbeans, and Spring. We had contacted the author of NiCad regarding the issues. They found that it was a problem of long file paths which will be fixed in the next NiCad releases. As a result, we did not have NiCad clones from these project in the agreed clone pairs. Simian clones of the same projects also disappeared from the agreed clone pairs since they could not find matches.

@@

\begin{table}
	\centering
	\caption{Classification results of agreed and disagreed clone pairs.}
	\label{tab:classification_good_o}
	\small
	\resizebox{\columnwidth}{!}{%
		\begin{tabular}{l|r|r|r|r|r|r|r|r}
			\hline
			Set & A & A' & B & C & D  & E & F & Total \\ 
			\hline 
			\hline
			\multirow{1}{*}{\textit{good}}  & 1 & 0 & 4  & 3 & 58  & 6 & 2,189 & 2,261 \\
			\multirow{1}{*}{\textit{ok}}  & 8 & 0 & 29  & 10 & 9,158 & 35 & 82 & 9,322 \\
			\hline 
			\hline 
			\multirow{1}{*}{$S_D$} & 79 & 0 & 336 & 17 & 209 & 63 & 167 & 871 \\
			\hline
			\multirow{1}{*}{$N_D$} & 8  & 0 & 27 & 1 & 77 & 3 & 82 & 168 \\ 
			\hline
			\hline
			Total & 96 & 0 & 396 & 31 & 9,502 & 107 & 2,520 & 12,622 \\ 
			\hline
		\end{tabular} 
	}
\end{table}

>>>>

\begin{table}
	\centering
	\caption{Configurations of Simian and NiCad}
	\label{t:param_tuning}
%	\resizebox{\columnwidth}{!}{%
	\small
	\begin{tabular}{l|p{7cm}}
		\hline 
		Tool & Parameters \\
		\hline
		$S_D$ &  threshold=6, ignoreStringCase, \newline ignoreCharacterCase, ignoreModifiers \\ 
		\hline
		$S_E$ & threshold=5, ignoreIdentifiers, \newline ignoreIdentifierCase, ignoreStrings, \newline ignoreCharacters, ignoreSubtypeNames, \newline balanceSquareBrackets  \\ 
		\hline 
		$N_D$ & Blocks, MinLine=10, MaxLine=1000, UPI=0.30 \\
		\hline
		$N_E$ & Blocks, MinLine=5, MaxLine=604, UPI=0.20, \newline blind renaming, literal abstraction \\ 
		\hline 
	\end{tabular} %
%}
\end{table}

@@

\begin{table}
	\centering
	\caption{Statistics of clones found between Stack Overflow and Qualitas projects using Simian (\textit{S}) and NiCad (\textit{N}) with default (\textit{D}) and EvaClone (\textit{E}) configurations}
	\label{tab:raw_stats}
	\small
	\resizebox{\columnwidth}{!}{%
		\begin{tabular}{l|r|r|r|r}
			\hline
			Stats & \multicolumn{1}{c|}{$S_D$} & \multicolumn{1}{c|}{$S_E$} & \multicolumn{1}{c|}{$N_D$} & \multicolumn{1}{c}{$N_E$} \\
			\hline
			Snippets & 1,086 & 1,531 & 1,392 & 12,886 \\
			Total C$_{\textrm{\textit{pairs}}}$ & 67,570 & 63,635,844 & 632,855 & 251,449,849 \\
			Avg.~C$_{\textrm{\textit{pairs}}}$ & 62 & 41,565 & 455 & 19,356 \\
			Avg.~C$_{\textrm{\textit{size}}}$ & 7.72 & 4.79 & 9.84 & 5.33 \\
			Avg.~C$_{\textrm{\textit{\%}}}$ & 29\% & 28\% & 25\% & 21\% \\
			\hline
		\end{tabular} %
	}
\end{table}

@@

Agreed clone pairs are clone pairs that pass Bellon's good- or ok-match criteria and selected for manual investigation. Similar to the original study, we select a threshold \textit{p} of 0.7 for both \textit{good} and \textit{ok} pairs \cite{Bellon2007}. %The number of projects processed by the clone detection tools are listed in \Cref{tab:projects_missing}. 
We encountered NiCad failures with a few Qualitas projects. 
%\FIXME{Reported the errors to NiCad creator. Cordy said it might be a long-path problem. Should we try fixing?}  
$N_D$ could not detect clones in Hibernate due to clustering errors. $N_E$ generated renaming errors for 5 projects including Vuze, Hibernate, Myfaces, Netbeans, and Spring. We had contacted the author of NiCad regarding the issues. They found that there problems of long file paths and TXL grammars which will be fixed in the next NiCad releases. As a result, we did not have NiCad clones from these project in the agreed clone pairs. Simian clones of the same projects also disappeared from the agreed clone pairs since they could not find matches.

@@

\begin{table}
	\centering
	\caption{Classification results of agreed and disagreed clone pairs.}
	\label{tab:classification_good_o}
	\small
	\resizebox{\columnwidth}{!}{%
		\begin{tabular}{l|r|r|r|r|r|r|r|r}
			\hline
			Set & A & A' & B & C & D  & E & F & Total \\ 
			\hline
			\multirow{1}{*}{\textit{good}}  & 1 & 0 & 4  & 3 & 58  & 6 & 2,189 & 2,261 \\
			\multirow{1}{*}{\textit{ok}}  & 8 & 0 & 29  & 10 & 9,158 & 35 & 82 & 9,322 \\
			\multirow{1}{*}{$S_D$} & 79 & 0 & 336 & 17 & 209 & 63 & 167 & 871 \\
			\multirow{1}{*}{$N_D$} & 8  & 0 & 27 & 1 & 77 & 3 & 82 & 168 \\ 
			\hline
			Total & 96 & 0 & 396 & 31 & 9,502 & 107 & 2,520 & 12,622 \\ 
			\hline
		\end{tabular} 
	}
\end{table}
